%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lockwitz Resume - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (09/25/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Forked from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% https://v2.overleaf.com/project/5baa4da77cc1d62f41c76df1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Mike}{Lockwitz}{ \urlstyle{same}\url{lockdev.com} \\
\href{mailto:mlockwitz@gmail.com}{mlockwitz@gmail.com} | 720.336.3337
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Web Development}
\location{Programming:}
JavaScript \textbullet{}   CSS \textbullet{} HTML \textbullet{} LESS \\
SASS \textbullet{} PHP \textbullet{} JSON \textbullet{} XML \\
\vspace{1pt}
\location{Technologies:}
AngularJS 1.x \textbullet{} Gatsby.js \textbullet{} Leaflet \textbullet{} Ionic\\
Rails \textbullet{} jQuery \textbullet{} React \textbullet{} WordPress \\
lodash \textbullet{} underscore \textbullet{} handlebars \\
\vspace{1pt}
\location{UI Frameworks:}
Bulma \textbullet{} Foundation \textbullet{} BloomerJS \\
Bootstrap \textbullet{} Material UI \textbullet{} Semantic UI \\
\vspace{1pt}
\location{Tools:}
Webpack \textbullet{} Node.js \textbullet{} Gulp \textbullet{} Grunt \textbullet{} npm \\ Bowser \textbullet{} Yarn \textbullet{} Browserify  \textbullet{} Yeoman \\
\vspace{5pt}
\subsection{UI/UX}
\location{Process:}
User Research \textbullet{} User Interviews \textbullet{} User Stories \textbullet{} Concept Ideation \textbullet{} Focus Groups \textbullet{} User Journey Mapping \\
Prototyping \textbullet{} A/B + Multivariant Testing  \\
\vspace{1pt}
\location{Design:}
Interaction Prototypes \textbullet{} Information Architecture \textbullet{} Interface Layouts \\
\vspace{1pt}
\location{Tools:}
Sketch \textbullet{} Photoshop \textbullet{} Illustrator \\
LucidChart \textbullet{} Mural \textbullet{} Figma \\
Google Tag Manager \textbullet{} Google Analytics \\
HotJar \textbullet{} Crazy Egg \textbullet{} Inspectlet \\
\vspace{5pt}
\subsection{Product Management}
\location{Process:}
Scrum \textbullet{} Lean \textbullet{} Kanban \textbullet{} Human Centered Design \textbullet{} User-centered Design \\
Design Sprints \textbullet{} Waterfall \textbullet{} Agile \\
\vspace{1pt}
\location{Tools:}
Jira \textbullet{} Confluence \textbullet{} Trello \textbullet{} GitHub Projects \textbullet{} Google Docs \textbullet{} Excel \textbullet{} Slack \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Purdue University}
\descript{BS in Computer and\\
Information Technology}
\location{2007 | West Lafayette, IN}
Conc. in Systems Analysis and Design \\
Minors in Business + Communications \\
\location
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/mikelockz}{\custombold{mikelockz}} \\
LinkedIn://  \href{https://www.linkedin.com/in/mlockwitz}{\custombold{mlockwitz}} \\
Twitch://  \href{https://www.twitch.tv/mikelockwitz}{\custombold{mikelockwitz}} \\
CodePen://  \href{https://codepen.io/MikeLockz/}{\custombold{MikeLockz}}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Flourish Systems, LLC}
\descript{| Front End Architect }
\location{Nov 2016 – Present | Denver, CO}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Develop and maintain AngularJS webapp to monitor and control scalable commercial agriculture hardware product optimized to reduce costs. \item Integrate Rails API via websockets and continuous delivery via Heroku. \item Build interactive UI framework of over 20 styled components and directives. \end{tightemize}
\sectionsep

\runsubsection{Influence Technologies, LLC}
\descript{| Technical Business Analyst }
\location{June 2016 – Sep 2018 | Denver, CO}
\begin{tightemize}
\item Managed process, internal teams, and client interaction from requirements gathering to design to implementation to maintenance of multi-year projects. \item Released open source js library (ivx.js) with team of developers and designers to reduce implementation time of interactive video marketing products. \item Translated business requirements from external stakeholders to functional specifications for internal teams and ensure accurate and timely delivery.\end{tightemize}
\sectionsep

\runsubsection{Influence Technologies, LLC}
\descript{| Senior Web Developer }
\location{Sep 2012 – June 2016 | Denver, CO}
\begin{tightemize}
\item Delivered web apps for global fortune 200 companies with 100+ million users.\item Built internal and external AngularJS dashboards connected to  .NET backend.\item Developed 30+ interactive video experiences optimized for lead conversion.\end{tightemize}
\sectionsep

\runsubsection{LockDev Ltd.}
\descript{| Owner}
\location{Mar 2012 – Present | Remote}
\begin{tightemize}
\item Contract front end development service for custom small business  microsites. \end{tightemize}
\sectionsep

\runsubsection{Open Bike}
\descript{| Founder and Evangelist}
\location{Jun 2012 – Oct 2014 | Denver, CO}
\begin{tightemize}
\item Developed multi-platform software prototypes to encourage bicycling as a viable commuter strategy by providing useful route information to cyclists. \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Community
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Community}
\runsubsection{Refresh Denver}
\descript{| Organizer}
\location{Jan 2014 – Present | Denver, CO}
\begin{tightemize}
\item Grown local design-focused meetup from 400 to over 4,000 current members.\item Host over 70 events with presentations by industry leaders  and experts.\item Organize more than 20 sponsors, multiple event venues for community group.
\end{tightemize}
\sectionsep

\runsubsection{Coder Dojo Denver}
\descript{| Mentor}
\location{Mar 2014 – Present | Denver, CO}
Teach students 8-17 years old the basics of web development using internationally developed curriculum specifically for encouraging youth interest in coding.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Extrancurricular
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurricular}
\begin{tabular}{rlll}
2018 & Participant & putup  & ETHDenver Hackathon \\
2017 & Best UI & safe-exchange  & CapitalOne DevExchange Hackathon\\
2016 & 2\textsuperscript{nd}/200+ & HostMagic  & AT\&T Developer Hackathon \\
2014 & 1\textsuperscript{st} Place & CraftedHere  & MJStartup Hackathon \\
2014 & 1\textsuperscript{st} Place & GovSafe  & Google GovDev Challenge \\
2013 & 1\textsuperscript{st} Place & FloodForecast & Esri Climate Resilience App Challenge\\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}
